\section{Publications}

My academic publications are listed on  \href{https://scholar.google.com.br/citations?user=STk6opQAAAAJ}{Google Scholar}. Currently, I have a first-author h-index of $6$.

{\sl Theses}

\begin{itemize}
	\item[--] L. N. Ribeiro, ``\href{http://www.repositorio.ufc.br/bitstream/riufc/16516/1/2016_dis_lnribeiro.pdf}{On supervised multilinear filtering: applications to system identification and antenna beamforming},'' 2016, Master's thesis. Advised by prof. A. L. F. de Almeida and prof. J. C. M. Mota;
	\item[--] L. N. Ribeiro, ``\href{https://github.com/lnribeiro/lnribeiro.github.io/blob/master/assets/pdf/rapport.pdf}{Tensor models applied to atrial fibrillation analysis},'' 2014, Master's thesis. Advised by prof. V. Zarzoso and prof. G. Favier;
	\item[--] L. N. Ribeiro, ``\href{https://github.com/lnribeiro/lnribeiro.github.io/blob/master/assets/pdf/monografia.pdf}{Separação cega de fontes: métodos e aplicações},'' 2014, Bachelor's thesis. Advised by prof. A. L. F. de Almeida and prof. J. C. M. Mota.
\end{itemize}

{\sl Papers}

\begin{enumerate}
	\item L. N. Ribeiro, S. Schwarz, A. L. F. de Almeida, ``\href{https://arxiv.org/abs/1907.08750}{Double-sided massive MIMO transceivers for mmWave Communications},'' under review. 
	
	\item L. N. Ribeiro, A. L. F. de Almeida, J. C. M. Mota, ``\href{https://doi.org/10.1016/j.sigpro.2018.12.010}{Separable linearly constrained minimum variance beamformers},'' Signal Processing, v. 158, pp. 15-25, 2019;
	
	\item L. N. Ribeiro, A. L. F. de Almeida, J. A. Nossek, J. C. M. Mota, ``\href{https://doi.org/10.1049/iet-spr.2018.5115}{Low-complexity separable beamformers for massive antenna array systems},'' IET Signal Processing, v. 13, pp. 434-442, 2019;
	
	\item L. N. Ribeiro, S. Schwarz, M. Rupp, A. L. F. de Almeida, ``\href{https://doi.org/10.1109/JSTSP.2018.2824762}{Energy efficiency of mmWave massive MIMO precoding with low-resolution DACs},'' IEEE Journal of Selected Topics in Signal Processing, v. 12, pp. 298-312, 2018;
	
	\item L. N. Ribeiro, J. C. M. Mota, A. L. F. de Almeida, ``\href{http://rtic.com.br/index.php/rtic/article/view/65}{Processamento Tensorial de sinais aplicado às comunicações},'' Revista de Tecnologia da Informação e Comunicação, v. 5, pp. 14-18, 2015.
\end{enumerate}

\newpage
{\sl Conference Proceedings}

\begin{enumerate}
	\item L. N. Ribeiro, A. L. F. de Almeida, Jo\~ao C. M. Mota, ``Low-rank tensor MMSE equalization,'' accepted at the 16th IEEE International Symposium on Wireless Communication Systems (ISWCS), 2019, Oulu, Finland;
			
	\item L. N. Ribeiro, A. L. F. de Almeida, N. J. Myers, R. W. Heath Jr., ``\href{https://doi.org/10.1109/ICASSP.2019.8683496}{Tensor-based estimation of mmWave MIMO channels with carrier frequency offset},'' 41th International Conference on Acoustics, Speech, and Signal Processing (ICASSP), 2019, Brighton, UK;
	
	\item L. N. Ribeiro, B. Sokal, A. L. F. de Almeida, J. C. M. Mota, ``\href{https://github.com/lnribeiro/lnribeiro.github.io/blob/master/assets/pdf/sbrt18.pdf}{Separable least mean squares beamforming},'' 36th Brazilian Symposium on Telecommunications (SBrT), 2018, Campina Grande, Brazil;
	
	\item L. N. Ribeiro, S. Schwarz, M. Rupp, A. L. F. de Almeida, J. C. M. Mota, ``\href{https://doi.org/10.23919/EUSIPCO.2017.8081651}{A low-complexity equalizer for massive MIMO systems based on array separability},'' 25th European Signal Processing Conference (EUSIPCO), 2017, Kos, Greece;
	
	\item L. N. Ribeiro, A. L. F. de Almeida, V. Zarzoso, ``\href{https://doi.org/10.1109/SAM.2016.7569709}{Enhanced block term decomposition for atrial activity extraction in atrial fibrillation ECG},'' 9th IEEE Sensor Array and Multichannel Signal Processing Workshop (SAM), 2016, Rio de Janeiro, Brazil;
	
	\item L. N Ribeiro,  A. L. F. de Almeida, J. M. M. Mota, ``\href{https://doi.org/10.1109/ICASSP.2016.7472221}{Tensor beamforming for multilinear translation invariant arrays},'' 41st International Conference on Acoustics, Speech, and Signal Processing, 2016 (ICASSP), Shanghai, China;
	
	\item  L. N. Ribeiro, A. R. Hidalgo-Mu\~{n}oz, G. Favier, J. C. M. Mota, A. L. F. de Almeida,  V. Zarzoso, ``\href{https://doi.org/10.1109/EUSIPCO.2015.7362850}{A tensor decomposition approach to noninvasive atrial activity extraction in atrial fibrillation ECG},'' 23rd European Signal Processing Conference (EUSIPCO), 2015, Nice, France;
	
	\item L. N. Ribeiro, A. R. Hidalgo-Mu\~{n}oz, V. Zarzoso, ``\href{https://doi.org/10.1109/EMBC.2015.7320000}{Atrial signal extraction in atrial fibrillation electrocardiograms using a tensor decomposition approach},'' 37th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC), 2015, Milan, Italy;
	
	 \item L. N Ribeiro,  A. L. F. de Almeida, J. M. M. Mota, ``\href{https://doi.org/10.1109/CAMSAP.2015.7383768}{Identification of separable systems using trilinear filtering},'' IEEE 6th International Workshop on Computational Advances in Multisensor Adaptive Processing (CAMSAP), 2015, Canc\'{u}n, Mexico;
	
	 \item L. N Ribeiro, J. M. M. Mota, A. L. F. de Almeida, ``\href{https://github.com/lnribeiro/lnribeiro.github.io/blob/master/assets/pdf/sbrt13.pdf}{Trilinear Wiener Filtering: application to equalization problems},''  31st Brazilian Symposium on Telecommunications (SBrT), 2013, Fortaleza, Brazil.
\end{enumerate}